%-------------------------
% Rover Resume - Fancy Template
% Link: https://github.com/subidit/rover-resume
%------------------------

\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{inter} % https://tug.org/FontCatalogue/
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
a4paper,
top=1.8cm,
bottom=1in,
left=2.5cm,
right=2.5cm
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=0pt..1.5em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}

\usepackage[dvipsnames]{xcolor}
% \usepackage[dvipsnames, svgnames, x11names]{xcolor} 
% \usepackage[dvipsnames]{xcolor} % xcolor.pdf Sec.4 Colors by Name
\colorlet{icnclr}{gray}
% \colorlet [⟨type⟩]{⟨name⟩}[⟨num model⟩]{⟨color ⟩}
% \definecolor[⟨type⟩]{⟨name⟩}{⟨model-list⟩}{⟨spec-list⟩}


\usepackage{titlesec}
% \titlespacing{command}{left spacing}{before spacing}{after spacing}[right]
% \titlespacing{\section}{0pt}{*3}{*1}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
% \titleformat{<command>}[<shape>]{<format>}{<label>}{<sec>}{<before-code>}[<after-code>]  
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\large\fontseries{semibold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\large\fontseries{medium}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}


\usepackage{fontawesome5}

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ % https://en.wikibooks.org/wiki/LaTeX/Hyperlinks
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={My Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							
\cfoot{\color{darkgray} Rover R\'esum\'e -- Page \thepage{} of \totalpages}


\begin{document}

%== HEADER ==%
\begin{center}
    {\fontsize{36}{36}\selectfont\interthin PETRARU\interheavy DENIS-MIHAI} \\ \bigskip
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:hi@example.com}{denispetraru76@gmail.com  } $|$ 
    {\color{icnclr}\faIcon{mobile-alt}} \href{tel:1234567890}{+40 755 562 530  } $|$
    {\color{icnclr}\faLinkedinIn} \href{https://www.linkedin.com/}{https://www.linkedin.com/in/denis-mihai-petraru-39635322b/}
\end{center}

\section{Education}
%==============
\subsection{Master's Degree $|$ {\normalfont\textit{Faculty of Economics and Business Administration - UAIC  }} }
\begin{itemize}
    \item M.S. in Business Information Systems \hfill \textbf{Iași, Oct. 2024-Present}
    \item Related Coursework: Mobile Applications in Business, Big Data and Machine Learning Tools, Multitier Application Development, Decision Support Systems, Project Management 
\end{itemize}
\subsection{Bachelor's Degree $|$ {\normalfont\textit{Faculty of Economics and Business Administration - UAIC  }} }
\begin{itemize}
    \item B.S in Informatics Economics \hfill \textbf{Iași, Oct. 2020-June 2023}
    \item Related Coursework: Object Oriented Programming, Data Structures , Database Administration, Computer Networks, Web Technologies 
\end{itemize}

\subsection{ High school degree $|$ {\normalfont\textit{Theoretic high school "Miron Costin”    }}}
\begin{itemize}
    \item B.S in Mathematical Informatics   \textbf{\hfill Iași, Sept. 2016-June 2020}
    \item Related Coursework: c++, pseudocode
\end{itemize}

\section{Experience}
%===================
\subsection{IDnow \hfill Oct. 2024 -- Dec. 2024}
\subsubsection{ Customer Service Agent \hfill Iași}
\begin{itemize}
    \item Performed identity verification checks by analyzing ID documents and detecting potential fraud attempts in compliance with KYC (Know Your Customer) regulations.   
    \item   Ensured the authenticity and consistency of personal information across multiple documents and sources.
    \item Maintained high attention to detail and confidentiality while processing sensitive client information in a fast-paced environment.  
    \item Collaborated with international teams and adhered to strict compliance and quality assurance protocols. 
\end{itemize}
\subsection{Cegeka Academy \hfill Feb. 2023 -- May 2023}
\subsubsection{ Intern .NET \hfill Iași}
\begin{itemize}
    \item  Implemented an online auction platform utilizing .NET and Blazor frameworks for the frontend, coupled with backend development powered by .NET technologies.   
    \item Designed a product listing page for the auction site, incorporating a search bar and filters to enhance user navigation and streamline the bidding experience.
    \item Completed diverse training modules encompassing C\# fundamentals, .NET, Blazor, API development, software testing, algorithm design, and database management. Also gained practical experience with Postman for API testing.  
    \item Presented a demo of the application in front of all teams involved in the development, at the end of a two weeks sprint. 
\end{itemize}

\section{Skills}
%===============
\begin{description}
    \item[Back‑end:]SOLID Design Principles, Microsoft Azure, Object-Oriented Programming (OOP), .NET Framework, ASP.NET, Blazor, Azure DevOps Services, Postman, C\#, Finance, PostgreSQL 
    \item[Front-end:]Object-Oriented Programming (OOP), Computer Science, C\#, C++, JavaScript, HTML, Cascading Style Sheets (CSS) 
\end{description}

\section{Projects}
%=================
\subsection{Online Store {\normalfont $|$ \href{https://github.com/den007s/denisprojects/blob/main/proiect-denispetraru\%20(2).zip}{\textit{GitHub Repository}}}}
\begin{itemize}
    \item This project is an online store made for the Introduction to CSS and HTML.
\end{itemize}
\subsection{Databases of an animal shelter {\normalfont $|$ \href{https://github.com/den007s/denisprojects/tree/main/Animal\%20Shelter}{\textit{GitHub Repository}}} }
\begin{itemize}
    \item In this project we had to make the databases of an animal shelter.
\end{itemize}


\end{document}